---
title: "Analysis"
author: "Sarah"
date: "4 February 2020"
output: html_document
---

```{r setup, include=FALSE, }
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Introduction
The aim of this analysis is to determine the effect of patient genotype and their glutathione (GSH) concentration on their sensitivty to cytotoxic (anti-cancer) drugs. Previous research has displayed that patients respond differently to anti-cancer drugs and that sensitivity can be implicated by both genotype and GSH concentration.

Researchers measured treatment sensitivity and GSH concentration for patients that had one of three alleles (*A2*,*AA01*,*B34*). The data is comprised of the following three variables:

**GSH**: a continuous measure glutathione concentration
**sens**: a continuous measure of treatment sensitivity in arbitrary units
**genotype**: a factor with three levels,A2, AA01 and B34

# Methods - leave

# Results

# direction and magnitude of output - effect of sensitivty and effect of genotype
# input each data section ino the grey boxes



```{r cars, echo=FALSE, warning=FALSE, message=FALSE}
m <- mean(cars$dist)
response <- read.table("response.txt", skip = 6, header = TRUE)
str(response)
mod <- lm(data = response, sens ~ GSH * genotype)
summary(mod)

anova(mod)

mod_2  <- update(mod, .~. -GSH:genotype)

summary(mod_2)
```

The **mean** *distance* is 'r m' and it is big and $p = \chi{2}

gsh effects sesn (df = 'r res$df[1], 'r res$df[3])


```{r}

```


